---
title: "Assignment_3"
author: "Sunil S"
date: "11 September 2017"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE))

O = c(8,47,34,11)
n=207
E = c(21,109,62,15)

degf = 3 # Sample size -1
```

### Converting sample responses to percentage as Population data (observed data) is in percentage
```{r, include = FALSE}
E = (E*100)/207

```
H0, Null Hypothesis is local responses from the survey are not same as expected frequencies of national survey
H1, ALternate Hypothesis is local responses from the survey are same as expected frequencies of national survey 

### Finding chisq critical value at 95% confidence level or 5% significance level
```{r, include =FALSE}
Chisq_crit = qchisq(p = 0.95,df = degf)
Chisq_crit 
```
### Finding Chisq test statistic value
```{r}
Chisq_test = sum((O-E)^2/E)
Chisq_test
```
As Chisq_test =3.5527 and Chisq_crit is 7.8147, Chisq_test is not in the critical region and hence we do not have enough evidence to accept Null hypothesis. That is local responses are not same as national survey. 